---
title: "Heatmap Visualisation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Heatmap Visualisation}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
library(ggplot2)
knitr::opts_chunk$set(fig.dpi = 96, collapse = TRUE, comment = "#>")
```

This vignette summarises the heatmap visualisation in the `ClickViz` package.  

## Input Data

The input data for the function `plot_transition_heatmap` will need to be in the following format. Similar to the `clickstreams` package, the data must be read using the following function `clickstreams:readClickstream(file)`.

Example data is available in the package as follows:

    ```{r}
    library(ClickViz)
    clickstreams[1:5]
    ```

## Plot Transition Matrix

The `plot_transition_heatmap` function calculates the Markov chain probabilities for the data provided. Axis labels and colour is added corresponding to the transition probabilities in an interactive heatmap.

Here are examples of the heatmap visualisation of the first order Markov chain transition matrix, using data available in the package:

    ```{r}
    library(ClickViz)
    plot_transition_heatmap(clickstreams)
    ```

    ```{r}
    library(ClickViz)
    plot_transition_heatmap(clickstreams_large)
    ```
