---
title: "Heatmap Visualisation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Heatmap Visualisation}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
library(ggplot2)
knitr::opts_chunk$set(fig.dpi = 96, collapse = TRUE, comment = "#>")
```

This vignette summarises the heatmap visualisation in the `ClickViz` package.  

## Input Data

The input data for the function `plot_transition_heatmap` will need to be in the following format. Similar to the `clickstreams` package, the data must be in the format of `clickstreams:readClickstream(file)`.

    ```{r}
    library(ClickViz)
    clickstreams[1:5]
    ```

## Plot Transition Matrix

The `plot_transition_heatmap` function calculates the Markov chain probabilities for the data provided. Then labels and colours are added to reflect the probbailites and plotted in an interactive heatmap.

Examples of the heatmap visualisation of the first order Markov chain transition matrix:

    ```{r}
    library(ClickViz)
    plot_transition_heatmap(clickstreams)
    ```

    ```{r}
    library(ClickViz)
    plot_transition_heatmap(clickstreams_large)
    ```
