---
title: "Network Visualisation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

This vignette summarises the network visualisation in the `ClickViz` package.  

## Input Data

The input data for the function `prepare_network_edges` and `prepare_network_vertices` will need to be in the following format. Similar to the `clickstreams` package, the data must be in the format of `clickstreams:readClickstream(file)`.

    ```{r}
    library(ClickViz)
    clickstreams[1:5]
    ```

## Plot Transition Matrix

The `prepare_network_edges` function calculates the Markov chain probabilities for the data provided. 

The `prepare_network_vertices` function calculates 

Examples of the network visualisation of the first order Markov chain transition matrix:

    ```{r}
    library(ClickViz)
    labels <- c("Type1", "Type2", "Type2", "Type3")
    state <- c("H", "P", "D", "E")
    vertex_labels_example <- tibble::tibble(state=state,
                                            vertex_label=labels)
        
    edges <- prepare_network_edges(clickstreams, alpha=0.01)
    nodes <- prepare_network_vertices(clickstreams,
                                      vertex_labels=vertex_labels_example)
    plot_transition_network(edges,
                            nodes,
                            edge_width_factor=5,
                            edge_arrow_size=0.6,
                            edge_curve_factor=0.5,
                            vertex_size_factor=1.2,
                            legend_x_position=-3.0,
                            legend_y_position=-0.5)
    ```

    ```{r}
    library(ClickViz)
    labels = c("Content", "Purchasing", "Content", "Products", "Artificial",
                "Home", "Site Information", "Profile", "Products", "Artificial",
                "Products", "Profile", "Purchasing", "Purchasing")
    state <- c("A", "B", "C", "D", "E", "H", "I", "L", "P", "R", "S", "U", "X", "Y")
    vertex_labels_example <- tibble::tibble(state=state,
                                            vertex_label=labels)
    
    edges <- prepare_network_edges(clickstreams_large, alpha=0.01)
    nodes <- prepare_network_vertices(clickstreams_large,
                                      vertex_labels=vertex_labels_example)
    plot_transition_network(edges,
                            nodes,
                            edge_width_factor=3,
                            edge_arrow_size=0.6,
                            edge_curve_factor=0.5,
                            vertex_size_factor=0.41,
                            legend_x_position=-2.0,
                            legend_y_position=-0.5)
    ```
